---
title: "Similarity"
author: "Anton Könneke"
output:
  html_document:
    df_print: paged
---

In this article, I analyse whether the newsletter by conservative party leader 
Friedrich Merz (he refers to it as '#merzmail') and the AfDs press releases converge 
over time in rhetoric.

# Data Preparation
Before we can compare the press releases of CDU and AfD, the objects must be 
imported and combined into a quanteda document.

```{r setup}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
library(pacman)
p_load(tidyverse, quanteda, quanteda.textstats, readtext, quanteda.textmodels, ggforce, grid)
cdu <- read_csv("texts/cdu_articles.csv")
afd <- read_csv("texts/afd_articles.csv")
```

We can then take a first look at the data:
```{r inspect_afd}
head(afd)
```
For the AfD-Data, we have the source url, the author, the date, the fulltext and 
the headline.

```{r inspect_cdu}
head(cdu)
```
For the CDU we also have a subtitle and a primer. We care only for the date and the fulltext for now, 
but in order to make the data extendable, all column names should be harmonised by now already.


```{r}
colnames(afd)
colnames(cdu)

cdu <- cdu %>% 
  rename(fulltext = text)
```

Let's also add the spd.
```{r}
spd <- data.table::fread("texts/spd_press_releases.csv")
# remove author names
spd_authors <- c(spd$authors_1, spd$authors_2, spd$authors_3, spd$authors_4,
                 spd$authors_5, spd$authors_6, spd$authors_7, spd$authors_8) %>% 
  unique()
spd_authors <- spd_authors[!is.na(spd_authors)]

spd <- spd %>% 
  mutate(url = url,
         date = as.Date(meta_1, format= "%d.%m.%Y"),
         fulltext = fulltext) %>% 
  select(url, date, fulltext)
spd
```


We also need to convert the strings holding the dates to date variables.
```{r}
cdu <- cdu %>% 
  mutate(date = as.Date(date, format = "%d.%m.%Y"))

Sys.setlocale(locale = "de_DE")
afd <- afd %>% 
  mutate(day = str_extract(date, "^\\d+"),
         mon = str_match(date, "(?<=\\d{1}\\.\\s)\\w*")[,1],
         year = str_extract(date, "\\d{4}$"),
         date_fmt = paste(year, mon, day, sep =  "-"),
         date = as.Date(date_fmt, format = "%Y-%B-%e")) 
Sys.setlocale(locale = "en_US")
```


Now we can now merge the two datasets together.
```{r merge}
cdu$source = "CDU"
afd$source = "AfD"
spd$source = "SPD"

press_rel <- bind_rows(cdu, afd, spd)
```

By adding an identifier for the month, we can later on compare trends over time 
on a month-grouped dataset that will offer sufficient observations for relatively 
stable estimations.

```{r add_month}
press_rel <- press_rel %>% 
  mutate(month = lubridate::round_date(date, "month"))
```

# Frequency
Lets start by simply examining the activity of both parties over time:
```{r frequency}
party_colors <- 
  scale_color_manual("Party",
                     values = c("AfD" = "#009ee0", "CDU" =  "black"))

press_rel %>% 
  filter(month >= lubridate::ymd("2021-01-01")) %>% 
  summarise(n = n(), .by = c(month, source)) %>% 
  ggplot(aes(month, n, color = source))+
  geom_line(size = 1)+
  party_colors+
  theme_bw()
```

# Keyness
Now to the text analysis: lets begin by identifying words that are best able to
predict whether we are reading a CDU-Text or an AfD-Text. The typical quanteda
workflow is to create a corpus, clean the tokens and then create a document-
feature matric (dfm).

```{r clean}
press_corp <- corpus(press_rel, text_field = "fulltext")
press_tok <-
  tokens(
    press_corp,
    remove_punct = TRUE,
    remove_numbers = TRUE,
    remove_symbol = TRUE
  ) %>% 
  tokens_tolower()
press_tok <- tokens_remove(press_tok, pattern = c(stopwords("de")))
press_tok <- tokens_remove(
  press_tok,
  pattern =
    as.character(tokens(
      paste0(unique(press_rel$author), collapse = " "),
      remove_punct = TRUE,
      remove_numbers = TRUE,
      remove_symbol = TRUE
    ) %>% 
      tokens_tolower())
)
press_dfmat <- dfm(press_tok) %>% 
              dfm_trim(min_termfreq = 10, termfreq_type = "count",
                       max_docfreq = 0.05, docfreq_type = "prop")
```


```{r keyness, fig.retina=T, fig.asp=.9}
textstat_keyness(dfm_group(press_dfmat, groups = source)) %>% 
  quanteda.textplots::textplot_keyness()+
  coord_cartesian(xlim = c(-1200, 1200))+
  ggtitle("AfD vs. CDU Keyness")
```

# Similarity
Lets now compute the similarity of the documents.
```{r similarity}
textstat_simil(dfm_group(press_dfmat, groups = source), 
               margin = "documents", 
               method = "correlation") %>% 
  head()
```
There is a certain degree of similarity, but we can not really interpret it by now.
After all, both sources talk in the same language about the same topic (politics).
Hence, it is not surprising that we find some correlation. However, what we 
can interpret are evolutions of this correlation. Does it change over time?

```{r simil_time}
press_dfmat$party_mon = paste(press_dfmat$source, press_dfmat$month, sep = "_")

simil_mon <- textstat_simil(
  dfm_weight(
    dfm_group(press_dfmat, groups = party_mon),
    "prop"),
               margin = "documents", 
               method = "correlation") %>% 
  as.data.frame() %>% 
  mutate(d1p = str_sub(document1, 1L, 3L),
         d2p = str_sub(document2, 1L, 3L),
         d1d = str_sub(document1, 5L, 14L),
         d2d = str_sub(document2, 5L, 14L)) %>% 
  filter(d1p == "AfD" & d2p == "CDU") %>% 
  filter(d1d == d2d) %>% 
  mutate(mon = lubridate::ymd(d1d))

ggplot(simil_mon, aes(mon, correlation))+
  geom_line()+
  geom_smooth()
```


```{r wordfish}
press_dfmat <- dfm(press_tok) %>% 
              dfm_trim(min_termfreq = 10, termfreq_type = "count",
                       max_docfreq = 0.05, docfreq_type = "prop")

press_dfmat <- dfm_subset(press_dfmat, date > as.Date("2020-01-01"))
press_dfmat$party_mon = paste(press_dfmat$source, press_dfmat$month, sep = "_")

wf <- quanteda.textmodels::textmodel_wordfish(
  x = dfm_group(press_dfmat, groups = party_mon),
  dir = c(1,2))

quanteda.textplots::textplot_scale1d(wf, margin = "documents")
quanteda.textplots::textplot_scale1d(wf, margin = "features",
                                     highlighted = c("impfzwang", "muezzins",
                                                     "masseneinwanderung",
                                                     "steuerwettbewerb",
                                                     "schutzmaßnahmen",
                                                     "asyl",
                                                     "antifa",
                                                     "cancel"))



tibble(
  psi = wf$psi,
  beta = wf$beta,
  features = wf$features) %>% 
  arrange((beta))

tibble(
  doc = wf$docs,
  theta  = wf$theta,
  se = wf$se.theta,
  date = wf$x@docvars$month,
  party = wf$x@docvars$source
) %>% 
  mutate(hi = theta + (se*1.96),
         lo = theta - (se*1.96)) %>% 
  ggplot(aes(date, theta, shape = party, color = party,
             ymin = lo, ymax = hi))+
  geom_pointrange()+
  theme_bw()+
  annotate(
    "curve",
    xend = as.Date("2022-01-15"),
    yend = -0.25,
    x = as.Date("2022-07-10"),
    y = 0.25,
    curvature = .5,
    arrow = arrow()
  ) +
  annotate(
    "text",
    x = as.Date("2022-07-10"),
    y = 0.1,
    label  = "Friedrich Merz\nwird CDU-Vorsitzender",
    hjust = "left",
    vjust = "bottom"
  ) 
```

