---
title: "wordfish_bund"
author: "Anton Könneke"
output:
  html_document:
    df_print: paged
---

This is an analysis of party positions over time that relies on party's press 
releases and wordfish.

# Data preperation
I use the press releases of the bundestag factions of CDU, Greens, SPD and AfD for now. 
All press releases were scraped from the respective websites and are available in this repo. 
Before I conduct the analyses, stopwords, author's names and partynames should be
deleted. The documents need to be harmonised with regards to covariates, mainly dates.

```{r setup}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
library(pacman)
p_load(tidyverse, quanteda, quanteda.textstats, readtext, quanteda.textmodels, ggforce, grid)
cdu <- read_csv("texts/cdu_articles.csv", show_col_types = FALSE)
afd <- read_csv("texts/afdbt_articles.csv", show_col_types = FALSE)
spd <- read_csv("texts/spd_press_releases.csv", show_col_types = FALSE)
greens <- readRDS("texts/greensbt_press.RDS")
```

We can then take a first look at the data:
```{r inspect_afd}
lapply(list(cdu, afd, spd, greens), colnames)
```
There are different nameing conventions that should be harmonised. I mainly need
 `date` and `fulltext`.
```{r harmonise}
# afd quiete annoyingly could not stick to a formating style....
Sys.setlocale(locale = "de_DE") # for month recognition
afd <- afd %>% 
  select(date, date2, title, prompt, fulltext, url) %>% 
  mutate(date3 = str_extract(fulltext, regex("(?<=Berlin,\\s)\\d+\\.\\s\\w*\\s\\d{4}")),
         date4 = str_extract(prompt, regex("(?<=Berlin,\\s)\\d+(\\.\\s|\\s)\\w*\\s\\d{4}")),
         date4 = ifelse(str_detect(date4, "\\."), 
                        as.Date(str_extract(date4, "\\d+\\.\\s\\w*\\s\\d{4}"), format = "%e. %B %Y"),
                        as.Date(str_extract(date4, "\\d+\\s\\w*\\s\\d{4}"), format = "%e %B %Y")),
         date4 = as.Date(date4),
         across(c(date, date2, date3), ~as.Date(str_extract(.x, "\\d+\\.\\s\\w*\\s\\d{4}"), format = "%e. %B %Y")),
         date = coalesce(date, date2, date3, date4)) %>% 
  select(!c(date2, date3, date4)) %>% 
  mutate(author = str_extract(title, regex("^.*(?=\\:)")),
         author = ifelse(str_detect(author, "\\:"), 
                          str_extract(author, regex("^.*(?=\\:)")),
                          author)) 

afd_authors <- unique(afd$author)

afd <- afd %>% 
  select(url, date, fulltext)

# its simpler for the cdu
cdu <- cdu %>% 
  rename(fulltext = text) %>% 
  mutate(date = as.Date(date, "%e.%m.%Y")) %>% 
  select(url, date, fulltext)

# spd
# store authornames in vector
spd_authors <- c(spd$authors_1, spd$authors_2, spd$authors_3, spd$authors_4,
                 spd$authors_5, spd$authors_6, spd$authors_7, spd$authors_8) %>% 
  unique()
spd_authors <- spd_authors[!is.na(spd_authors)]

spd <- spd %>% 
  mutate(url = url,
         date = as.Date(meta_1, format= "%d.%m.%Y"),
         fulltext = fulltext) %>% 
  select(url, date, fulltext)


# greens
greens <- greens %>% 
  mutate(date = as.Date(date, "%d.%m.%Y")) %>% 
  select(url, date, fulltext)
```


Now we can now merge the two datasets together.
```{r merge}
cdu$source = "CDU"
afd$source = "AfD"
spd$source = "SPD"
greens$source = "Greens"

press_rel <- bind_rows(cdu, afd, spd, greens)
```

By adding an identifier for the month, we can later on compare trends over time 
on a month-grouped dataset that will offer sufficient observations for relatively 
stable estimations.

```{r add_month}
press_rel <- press_rel %>% 
  mutate(month = lubridate::round_date(date, "month"))
```

# Frequency
Lets start by simply examining the activity of both parties over time:
```{r frequency}
party_colors <- 
  scale_color_manual("Party",
                     values = c("AfD" = "#009ee0", "CDU" =  "black", "SPD" = "red",
                                "Greens" = "forestgreen"))

press_rel %>% 
  filter(month >= lubridate::ymd("2021-01-01")) %>% 
  summarise(n = n(), .by = c(month, source)) %>% 
  ggplot(aes(month, n, color = source))+
  geom_line(size = 1)+
  party_colors+
  theme_bw()
```

# Preprocessing
```{r clean}
press_corp <- corpus(press_rel, text_field = "fulltext")
press_tok <-
  tokens(
    press_corp,
    remove_punct = TRUE,
    remove_numbers = TRUE,
    remove_symbol = TRUE,
    remove_separators = TRUE,
    split_hyphens = T,
    remove_urls = T
  ) %>% 
  tokens_tolower()
press_tok <- tokens_remove(press_tok, pattern = c(stopwords("de")))

# remove names from BT-Members
mdbs <- btmembers::import_members()
mdbs19_20wp <- mdbs$wp %>% 
  filter(wp %in% c(19, 20)) %>% pull(id)

mdb_names <- mdbs$namen %>%
  filter(id %in% mdbs19_20wp) %>%
  mutate(name = paste(vorname, nachname, sep = " ")) %>% 
  pull(name) 

mdb_names <- tokens(paste(mdb_names, collapse = " "),
    remove_punct = TRUE,
    remove_numbers = TRUE,
    remove_symbol = TRUE,
    remove_separators = TRUE
  ) %>% tokens_tolower()

press_tok <- press_tok %>% 
  tokens_remove(mdb_names) %>% 
  tokens_remove(c("cdu", "afd", "spd", "grüne", "fraktion", "sprecher"))

press_dfmat <- dfm(press_tok) %>% 
              dfm_trim(min_termfreq = 10, termfreq_type = "count",
                       max_docfreq = 0.1, docfreq_type = "prop")
```

# Wordfish
```{r wordfish}
press_dfmat <- dfm_subset(press_dfmat, date > as.Date("2022-01-01"))
press_dfmat$party_mon = paste(press_dfmat$source, press_dfmat$month, sep = "_")

wf <- quanteda.textmodels::textmodel_wordfish(
  x = dfm_group(press_dfmat, groups = party_mon),
  dir = c(1,2))

quanteda.textplots::textplot_scale1d(wf, margin = "documents")
quanteda.textplots::textplot_scale1d(wf, margin = "features",
                                     highlighted = c("impfzwang", "muezzins",
                                                     "masseneinwanderung",
                                                     "steuerwettbewerb",
                                                     "schutzmaßnahmen",
                                                     "asyl",
                                                     "antifa",
                                                     "cancel"))



tibble(
  psi = wf$psi,
  beta = wf$beta,
  features = wf$features) %>% 
  arrange((beta))

tibble(
  doc = wf$docs,
  theta  = wf$theta,
  se = wf$se.theta,
  date = wf$x@docvars$month,
  party = wf$x@docvars$source
) %>% 
  mutate(hi = theta + (se*1.96),
         lo = theta - (se*1.96)) %>% 
  ggplot(aes(date, theta, shape = party, color = party,
             ymin = lo, ymax = hi))+
  geom_pointrange()+
  geom_smooth(se = F)+
  theme_bw()+
  annotate(
    "curve",
    xend = as.Date("2021-12-17"),
    yend = -0.25,
    x = as.Date("2022-07-10"),
    y = 0.25,
    curvature = .5,
    arrow = arrow()
  ) +
  annotate(
    "text",
    x = as.Date("2022-07-10"),
    y = 0.25,
    label  = "Friedrich Merz\nwird CDU-Vorsitzender",
    hjust = "left",
    vjust = "bottom"
  ) +
  party_colors
```